Constant-round Blind Classical Verification of Quantum Sampling

### 2020-08-22 qpip0.tex
cite measurement protocol binding property

\begin{lemma}[binding property of $\PiMeasure$]
	\label{lem:urmila-binding}
	Let $\PMeasureStar$ be a $\BQP$ cheating prover for $\PiMeasure$ and $\lambda$ be the security parameter. Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
	\iffalse    
	Suppose that for all $\lambda\in\bbN$ and $h\in\zo^*$ \Ethan{or $\zo^n$?},
	$\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$.
	Then, under the QLWE assumption, there exists some $\rho$ so that for all $h$,
	The verifier's output on the Hadamard round is $\negl(\lambda)$-computationally indistinguishable from $M_{XZ}(\rho, h)$.
	\fi
\end{lemma}

>>>>

\begin{lemma}[binding property of $\PiMeasure$; special case of Claim 7.1 in \cite{FOCS:Mahadev18a}]
	\label{lem:urmila-binding}
	Let $\PMeasureStar$ be a $\BQP$ cheating prover for $\PiMeasure$ and $\lambda$ be the security parameter. Under the QLWE assumption, if $\PMeasureStar$ passes the testing round with probability $1-\negl(\lambda)$ for all $h$, then there exists some $\rho$ so that for all verifier's input $h \in \zo^n$, the verifier's outputs on the Hadamard round is computationally indistinguishable from $M_{XZ}(\rho, h)$.
\end{lemma}
